Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-11-26 manuscript/manuscript.Rmd
sent to co-authors

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
description: A systematic review and meta-analysis
author: 
- name: Aaron Conway
  address: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
  url: https://www.aaronconway.info
- name: Megan Bittner
  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Dan Phan
  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Navpreet Kamboj
  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
- name: Kristina Chang
  address: Toronto General Hospital, UHN
- name: Peter Collins
  address: Toronto General Hospital, UHN
- name: Matteo Parotto
  address: Toronto General Hospital, UHN
date: "`r Sys.Date()`"
bibliography: bibliography.bib
output: distill::distill_article
---

@@

Zero-heat-flux thermometers are non-invasive devices that can be used to continuously monitor temperature. These devices are increasingly being used in clinical practice to substitute for invasive core temperature measurement during surgery and in critical care settings. The aim of this review was to determine the accuracy and precision of zero-heat-flux temperture measurements.

@@

Core temperature monitoring is an important intervention within perioperative and intensive care settings. Thermoregulatory dysfunction is commonly associated with the induction of anesthesia and can lead to adverse outcomes including cardiac dysrhythmias, altered hemostasis and increased risk of surgical site infection [@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect]. The pulmonary artery catheter is the reference standard for continuous core temperature monitoring, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue[@hadian2006evidence]. Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions.

Zero-heat-flux thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature. Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M SpotOn temperature monitoring system (3M, St Paul, MN), as a single-use, disposable sensor. In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and isinitially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues. Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature [@eshraghi2014].

@@

A systematic review was conducted in accordance with a predetermined protocol. The protocol was submitted to PROSPERO for registration but due to delays in processing we had started data extraction by the time it was reviewed. Therefore, the protocol did not meet the requirements for registration. A copy of the submitted protocol can be accessed [here](https://github.com/awconway/zhf-review). The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophaeal, bladder or rectal site. Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.

@@

Published studies were found by searching Medline and EMBASE from January 2000 to July 2019. The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should]. This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers. The search strategies used for each data base can be located [here](https://aconway.dev/zhf app). Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).

@@

Information was extracted regarding study characteristics (author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and temperature measurement characteristics (placement of sensor, timing and methods of measurements). The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature measurement between the zero-heat-flux and comparator thermometers. 
We also extracted information about how repeated measurements were handled. In particular we assessed whether studies: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].

Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2) [@whiting2011quadas]. Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias. We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry [@glasziou2001systematic]. Statistical approaches for detection of reporting bias were not conducted due to lack of validated methods [@begg2005systematic]. ASimulations have revealed that tests for detecting funnel plot asymmetry will result in publication bias being incorrectly identified too often [@deeks2005performance].

In order to rate the quality of evidence, we applied the Grading Quality of Evidence and Strength of Recommendation methodology [@schunemann2008grading]. Evidence was downgraded in accordance with study limitations, inconsistency and imprecision. There were no circumstances in which evidence was downgraded for indirectness as this systematic review only included relevant studies. Although the possibility of publication bias was not excluded, this bias was not formally assessed as it was not considered sufficient enough to reason downgrading the quality of evidence.

@@

The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the ZHF and established comparator thermometers. A framework for meta-analysis of Bland-Altman method comparison studies developed by @tipton2017framework based on limits of agreement approach was used. This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled LoAs in the population (not just in the samples studied). The ‘population LoA’ is more broad than the LoA commonly reported in the meta-analyses of Bland-Altman studies [@tipton2017framework]. Pooled limits of agreement were calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.

Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated standard errors estimated using robust variance estimation. Robust variance estimation was used alternatively to model-based standard errors as some studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small]. We used the method-of-moments estimator from @dersimonian1986meta for the $\tau2$ parameter.

Measures of uncertainty were included in our meta-analyses by calculating the outer 95% confidence intervals for pooled limits of agreement. We also accounted for repeated measurements if they were not properly adjusted for in individual studies. This was achieved by using weights proportional to the number of participants, not the total number of measurements.  The R statistical program was used to conduct all analyses [@team2017r]. All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zhf-review).

@@

The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 °C [@eshraghi2014]. It was deemed that outer confidence bounds for 95% LoA between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds wouldbe clinically unacceptable.

@@

A graphical overview of the findings for the primary analysis is presented in Figure \@ref(fig:fig-2). The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`°C. The population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies). The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency. Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` stsudies). The mean bias was again `r low_risk$bias_mean`°C with population limits of agreement spanning from `r low_risk$CI_L_rve`°C to `r low_risk$CI_U_rve`°C. A further sensitivity analysis excluding studies that received industry funding revealed population limits of agreement that were considerably wider than the primary analysis (`r conflict$CI_L_rve`°C to `r conflict$CI_U_rve`°C). The GRADE rating for this sensitivity was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.

<div class="l-screen-inset">

```{r fig-2, fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path=""}
include_graphics("gofer_core.png")
```

</div>

@@

<div class="l-page-outset">

```{r table-1}
ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- bind_rows(ma, .id="Comparison")
df %>% 
  rename("Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
    gt() %>% 
  tab_header(
    title = "Table 1. Results of meta-analyses"  )  %>% 
  tab_spanner(
    label = "Population limits of agreement",
    columns = vars(
      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
  )
```
</div>

@@

Results from this systematic review have important implications for practice. Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as one degree Celcius higher or lower than core temperature. It was reassuting that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QADAS-2 tool were similar. As such, it is vital for clinicians considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation. If so, then it may not be appropriate to substitute the zero-heat-flux device in place of a core thermometer.

Our estimates of the accuracy of zero-heat-flux thermometers are similar to results from a previous meta-analysis that compared other peripheral thermometers, such as sublingual and temporal artery devices, with core temperature measurements [@niven2015accuracy]. However, this previous meta-analysis used a statistical approach that did not incorporate the magnitude of heteroogeneity in results between studies or sampling error. As such, it is possible that the zero-heat-flux thermometer may still more precise than other peripheral thermometers.

@@

Although comparisons with core temperture are the most important to evaluate, we included studies that compared zero heat flux and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways non-invasive monitor temperature. Also, there may be situations where it is not practical to expose research participants to the potential additional risk of invasive core temperature monitoring for the purposes of evaluating the new temperature monitoring device when it is standard practice for only peripheral temperature monitoring to be used. Whether or not the zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear. Population limits of agreement calculated from four studies were broad, spanning from one degree less than zero heat flux temperature to one degree higher. Further studies are therefore required.

It should be noted that we did not include studies that used the Temple Touch Pro because it is not strictly a zero-heat-flux device. This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different. Far fewer studies have  evaluated the Temple Touch Pro compared to the zero-heat-flux device [@evron2017evaluation; @sastre2019evaluation].

Many studies in this review analysed a large number of measurements of temperature with relatively small sample sizes. Importantly, the approach we used for our meta-analysis takes this into account. By using robust variance estimation, weights for pooling estimates in the meta-analyis become proportional to the number of patients not the total number of measurements.[@tipton2017framework]

The accuracy of zero heat flux temperature monitoring has been evaluated in various intra-operative contexts as well as in the intensive care unit setting. Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting. Only one study included in our systematic review included pediatric patients. Additional studies to evaluate the accuracy of this device in children may be warranted to increase confidence.

@@

We did not extract data on adverse events due to zero-heat-flux temperature monitoring. The possibility of publication bias cannot be ruled out, although the evidence suggests this may not be as serious of a problem for studies that are not randomized controlled trials [@begg2005systematic]. Our focus for the meta-analysis was on calculating population limits of agreement, which incorporate the variation in bias between studies into the estimates. For this reason, we did not use meta-regression or tests for interaction between subgroups as a way to investigate sources of heterogeneity. It is important to note that this review did not assess the clinical utility of temperature monitoring using the zero-heat-flux device. The evidence from this review should be considered in the context of other information about the reliability and ease of use of this device.

@@

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
description: A systematic review and meta-analysis
author: 
- name: Aaron Conway
  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
  url: https://www.aaronconway.info
- name: Megan Bittner
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Dan Phan
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Navpreet Kamboj
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
- name: Kristina Chang
  affiliation: Toronto General Hospital, UHN
- name: Peter Collins
  affiliation: Toronto General Hospital, UHN
- name: Matteo Parotto
  affiliation: Toronto General Hospital, UHN
date: "`r Sys.Date()`"
bibliography: bibliography.bib
output: distill::distill_article
repository_url: https://github.com/awconway/zhf-review
twitter:
  creator: "@aw_conway"
---

@@

Zero-heat-flux thermometers are non-invasive devices that can be used to continuously monitor temperature. These devices are increasingly being used in clinical practice to substitute for invasive core temperature measurement during surgery and in critical care settings. The aim of this review was to determine the accuracy and precision of zero-heat-flux temperature measurements.

@@

Continuous core temperature monitoring is commonly used within perioperative and intensive care settings. Thermoregulatory dysfunction is commonly associated with the induction of anesthesia and can lead to adverse outcomes including cardiac arrhythmia, altered hemostasis and increased risk of surgical site infection.[@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect] The pulmonary artery catheter is the reference standard for continuous core temperature monitoring, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue.[@hadian2006evidence] Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions.

Zero-heat-flux thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature. Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M SpotOn temperature monitoring system (3M, St Paul, MN), as a single-use, disposable sensor. In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and is initially warmed to equilibrate the temperature of the skin surface to the underlying core tissues. Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature.[@eshraghi2014]

@@

A systematic review was conducted in accordance with a predetermined protocol. The protocol was submitted to PROSPERO for registration but due to delays in processing we had started data extraction by the time it was reviewed. Therefore, the protocol did not meet the requirements for registration. A copy of the submitted protocol can be accessed [here](https://github.com/awconway/zhf-review). The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder or rectal site. Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.

@@

Published studies were found by searching Medline and EMBASE from January 2000 to July 2019. The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers. The search strategies used for each data base can be located [here](https://aconway.dev/zhf app). Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).

@@

Information was extracted regarding study characteristics (author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and temperature measurement characteristics (placement of sensor, timing and methods of measurements). The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature measurement between the zero-heat-flux and comparator thermometers. 
We also extracted information about how repeated measurements were handled. In particular we assessed whether studies: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data.[@myles2007using]

Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2).[@whiting2011quadas] Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias. We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry.[@glasziou2001systematic] Statistical approaches for detection of reporting bias were not conducted due to lack of validated methods.[@begg2005systematic] Simulations have revealed that tests for detecting funnel plot asymmetry will result in publication bias being incorrectly identified too often.[@deeks2005performance]

In order to rate the quality of evidence, we applied the Grading Quality of Evidence and Strength of Recommendation methodology.[@schunemann2008grading] Evidence was downgraded in accordance with study limitations, inconsistency and imprecision. There were no circumstances in which evidence was downgraded for indirectness as this systematic review only included relevant studies. Although the possibility of publication bias was not excluded, this bias was not formally assessed as it was not considered sufficient enough to reason downgrading the quality of evidence.

@@

The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the ZHF and established comparator thermometers. A framework for meta-analysis of Bland-Altman method comparison studies developed by @tipton2017framework based on limits of agreement approach was used. This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled limits of agreement in the population (not just in the samples studied). The ‘population limits of agreement’ is more broad than the limits of agreement commonly reported in the meta-analyses of Bland-Altman studies.[@tipton2017framework] Pooled limits of agreement were calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.

Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated standard errors estimated using robust variance estimation. Robust variance estimation was used alternatively to model-based standard errors as some studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements[@hedges2010robust; @tanner2016handling; @tipton2015small] We used the method-of-moments estimator from @dersimonian1986meta for the $\tau2$ parameter.

Measures of uncertainty were included in our meta-analyses by calculating the outer 95% confidence intervals for pooled limits of agreement. We also accounted for repeated measurements if they were not properly adjusted for in individual studies. This was achieved by using weights proportional to the number of participants, not the total number of measurements.  The R statistical program was used to conduct all analyses[@team2017r] All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zhf-review).

@@

The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 °C.[@eshraghi2014] It was deemed that outer confidence bounds for 95% limits of agreement between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds would be clinically unacceptable.

@@

A graphical overview of the findings for the primary analysis is presented in Figure \@ref(fig:fig-2). The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`°C. The population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies). The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency. Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` studies). The mean bias was again `r low_risk$bias_mean`°C with population limits of agreement spanning from `r low_risk$CI_L_rve`°C to `r low_risk$CI_U_rve`°C. A further sensitivity analysis excluding studies that received industry funding revealed population limits of agreement that were considerably wider than the primary analysis (`r conflict$CI_L_rve`°C to `r conflict$CI_U_rve`°C). The GRADE rating for this sensitivity was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.

```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path=""}
include_graphics("gofer_core.png")
```

@@

```{r table-1, layout="l-page-outset"}
ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- bind_rows(ma, .id="Comparison")
df %>% 
  rename("Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
    gt() %>% 
  tab_header(
    title = "Table 1. Results of meta-analyses"  )  %>% 
  tab_spanner(
    label = "Population limits of agreement",
    columns = vars(
      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
  )
```

@@

Results from this systematic review have important implications for practice. Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as one degree Celsius higher or lower than core temperature. It was reassuring that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QADAS-2 tool were similar. As such, it is vital for clinicians considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation. If so, then it may not be appropriate to substitute the zero-heat-flux device in place of a core thermometer.

Our estimates of the accuracy of zero-heat-flux thermometers are similar to results from a previous meta-analysis that compared other peripheral thermometers, such as sublingual and temporal artery devices, with core temperature measurements.[@niven2015accuracy] However, this previous meta-analysis used a statistical approach that did not incorporate the magnitude of heterogeneity in results between studies or sampling error. As such, it is possible that the zero-heat-flux thermometer may still more precise than other peripheral thermometers.

@@

Although comparisons with core temperature are the most important to evaluate, we included studies that compared zero-heat-flux and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways non-invasive monitor temperature. Also, there may be situations where it is not practical to expose research participants to the potential additional risk of invasive core temperature monitoring for the purposes of evaluating the new temperature monitoring device when it is standard practice for only peripheral temperature monitoring to be used. Whether or not the zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear. Population limits of agreement calculated from four studies were broad, spanning from one degree less than zero-heat-flux temperature to one degree higher. Further studies are therefore required.

It should be noted that we did not include studies that used the Temple Touch Pro because it is not strictly a zero-heat-flux device. This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different. Far fewer studies have  evaluated the Temple Touch Pro compared to the zero-heat-flux device.[@evron2017evaluation; @sastre2019evaluation]

Many studies in this review analysed a large number of measurements of temperature with relatively small sample sizes. Importantly, the approach we used for our meta-analysis takes this into account. By using robust variance estimation, weights for pooling estimates in the meta-analysis become proportional to the number of patients not the total number of measurements.[@tipton2017framework]

The accuracy of zero-heat-flux temperature monitoring has been evaluated in various intraoperative-operative contexts as well as in the intensive care unit setting. Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting. Only one study included in our systematic review included pediatric patients. Additional studies to evaluate the accuracy of this device in children may be warranted to increase confidence.

@@

We did not extract data on adverse events due to zero-heat-flux temperature monitoring. The possibility of publication bias cannot be ruled out, although the evidence suggests this may not be as serious of a problem for studies that are not randomized controlled trials.[@begg2005systematic] Our focus for the meta-analysis was on calculating population limits of agreement, which incorporate the variation in bias between studies into the estimates. For this reason, we did not use meta-regression or tests for interaction between subgroups as a way to investigate sources of heterogeneity. It is important to note that this review did not assess the clinical utility of temperature monitoring using the zero-heat-flux device. The evidence from this review should be considered in the context of other information about the reliability and ease of use of this device.

@@

<script src="https://hypothes.is/embed.js" async></script>
